\bsection{Weapons}
\subsection*{Melee Weapons}
{\small \textbf{Axe (S):} Cutting Edge. \\
\textbf{Beastlash(S-1):} Beastbane, Reach. \\
\textbf{Brazier Iron(S+1):} Two-handed, Brazier Fire. \\
\textbf{Dagger (S):} +1 to enemy armour save. \\
\textbf{Double-Handed Weapon (S+2):} Two-handed, Strike last. \\
\textbf{Dwarf axe(S):} Cutting Edge, Parry. \\
\textbf{Fighting Claws (S):} Climb, Parry, Cumbersome. \\
\textbf{Fist (S-1):} +1 to enemy armour save. \\
\textbf{Flail (S+2):} Heavy, Two-handed. \\
\textbf{Gromril Weapon:} Extra –1 save modifier. \\
\textbf{Halberd (S+1):} Two-handed. \\
\textbf{Hammer, Staff, Mace or Club (S):} Concussion. \\
\textbf{Ithilmar Weapon:} Extra +1 initiative bonus. \\
\textbf{Lance (S+2):} Cavalry bonus. \\
\textbf{Morning Star (S+1):} Heavy, Difficult to use. \\
\textbf{Rapier(S):} Parry, Barrage, +1 to enemy armour save. \\
\textbf{Sigmarite Warhammer (S+1):} Concussion, Holy. \\
\textbf{Spear (S):} Strike first, S+1 Cavalry bonus. \\
\textbf{Squig Prodder(S):} Strike first, S+1 Cavalry bonus, keep Squigs 12”. \\
\textbf{Steel Whip (S):} Range 4”, No Parry, Reach. \\
\textbf{Sword (S):} Parry. \\
\textbf{Sword Breaked(S):} Parry, Trap Blade. \\
\textbf{Weeping Blades (S):} Pair, Venomous.}

\subsection*{Missile Weapons}
{\small \textbf{Blowpipe (8”-S1):} +1 Save, Poison, Stealthy. \\
\textbf{Blunderbuss (16”-S3):} Special Shot, Fire once. \\
\textbf{Bow (24”-S3):} Special Shot, Fire once. \\
\textbf{Crossbow (30”-S4):} Move or Fire. \\
\textbf{Crossbow Pistol (10”-S4):} Shoot once in melee. \\
\textbf{Duelling Pistol (10”-S4):} Accuracy, Prepare, Hand- to-hand , –2 Save. \\
\textbf{Elf Bow (36”-S3):} –1 Save. \\
\textbf{Handgun (24”-S4):} Prepare, Move/Fire, –2 Save. \\
\textbf{Hochland Long Rifle (48”-S4):} Prepare, –2 Save, Move/Fire, Pick Target. \\
\textbf{Long Bow} (30”-S3). \\
\textbf{Pistol (6”-S4):} Prepare shot, –2 Save modifier, Hand-to-hand \\
\textbf{Repeater Crossbow (24”-S3):} Fire Twice. \\
\textbf{Short Bow} (16”-S3). \\
\textbf{Sling (18”-S3):} Fire twice at half range. \\
\textbf{Throwing Star or Knife (6”-S):} Thrown weapon. \\
\textbf{Warplock Pistol (8”-S5):} –3 Save Modifier. Fire every other turn.}

\subsection*{Special Rules}
{\small \textbf{Accuracy:} +1 bonus on to hit rolls. \\
\textbf{Barrage:} retry attack if failed to wound at cumulative -1 to hit. \\
\textbf{Beastbane:} Fear to animals. \\
\textbf{Brazier Fire:} d6 on successful hit, on 5+ victim set on fire (4+ or S4 in recovery each turn, untill first save) \\
\textbf{Climb:} This weapon aids climbing. Add +1 to initiative when making climbing tests. \\
\textbf{Concussion:} In close combat a roll of 2–4 is treated as stunned when rolling on the injury chart. \\
\textbf{Cumbersome:} The user of this weapon may not use another weapon for the entire battle. \\
\textbf{Cutting Edge:} An extra save modifier of –1. \\
\textbf{Heavy:} The +2 Strength bonus only applies in the first turn of each hand-to-hand combat. \\
\textbf{Holy:} +1 bonus to all wound rolls against any Possessed or Undead models. \\
\textbf{Poison:} If a 6 is rolled to hit the weapon causes a wound, but cannot cause critical hits. \\
\textbf{Reach:} A model armed with such a weapon can and may attack figures out of base-to-base contact. The target may not strike back. \\
\textbf{Reach:} attack up to 4”. \\
\textbf{Stealthy:} The Assassin may remain hidden if the victim fails an initiative test. \\
\textbf{Strike First:} This weapon strikes first, even if charged, on the first turn of combat. \\
\textbf{Thrown weapon:} No penalty for range or moving. \\
\textbf{Trap Blade:} d6 after successful parry, on 4+ opponent's weapon breaks. \\
\textbf{Venomous:} as Black Lotus poison.}

\bsection{Critical Hits}
{\small A wound roll of 6 causes a critical hit. If the attacker normally needs 6s to
wound his target, he cannot cause a critical hit. Roll a D6
and consult the Critical Hit chart below. A model
may only cause one critical hit in each shooting and
hand-to-hand combat phase.}

\subsection*{Missile Weapons}
\textit{Bows, crossbows, blackpowder weapons, throwing knives etc.:}\\
\textbf{1–2 Hits a Weak Spot.} The missile penetrates its target’s armour. Ignore all armour saves.\\
\textbf{3–4 Ricochet.} If there are any other models within 6”, the closest enemy model is also hit. Roll to wound and take any saves as normal for both targets.\\
\textbf{5–6 Master Shot.} The missile hits an eye, the throat, or some other vulnerable part. The target suffers 2 wounds instead of 1. There is no armour save.

\subsection*{Bludgeoning Weapons}
\textit{Clubs, maces, hammers, flails, double-handed hammers etc.}\\
\textbf{1–2 Hammered.} The target is knocked off balance. Your opponent may not fight this turn if he hasn’t already fought.\\
\textbf{3–4 Clubbed.} The hit ignores armour saves and saves from helmets.\\
\textbf{5 Wild Sweep.} Your opponent’s weapon is knocked from his hand. If he is carrying two weapons, roll to see which one he loses. He must fight with whatever back-up weapon he has in his equipment for the rest of this combat (or fight unarmed if he has no other weapons). Roll to wound and take armour saves as normal.\\
\textbf{6 Bludgeoned.} The victim automatically goes out of action if he fails his armour save. Even if he has several wounds remaining, he will be taken out of action by this attack.

\subsection*{Bladed Weapons}
\textit{Swords, axes, double-handed swords etc.}\\
\textbf{1–2 Flesh Wound.} This attack hits an unprotected area, so there is no armour save.\\
\textbf{3–4 Bladestorm.} The warrior unleashes a virtual hail of blows. The attack causes 2 wounds instead of 1. Take armour saves separately for each wound. Remember that, as with other critical hits, if an attack causes multiple wounds for other reasons as well, you choose the highest number of wounds.\\
\textbf{5–6 Sliced!} The strike ignores armour saves, causes 2 wounds, and your warrior gains +2 to any Injury rolls.

\subsection*{Unarmed Combat}
\textit{Wardogs, warhorses, Zombies, Possessed, animals etc.}\\
\textbf{1–2 Body Blow.} Your opponent staggers, allowing you to seize the initiative and make an additional attack. Immediately roll to hit and to wound. Any saves are taken as normal.\\
\textbf{3–4 Crushing Blow.} The blow lands with tremendous force. You gain +1 to the Injury roll if your opponent fails his save.\\
\textbf{5–6 Mighty Blow.} With a mighty punch or flying kick, you send your opponent sprawling to the ground. The attack ignores armour saves and you gain +2 to any Injury rolls.

\subsection*{Thrusting Weapons}
\textit{Spears, halberds, lances etc.}\\
\textbf{1–2 Stab.} With a quick strike, you penetrate your opponent’s defences. You gain +1 to any Injury rolls. Armour saves are taken as normal.\\
\textbf{3–4 Thrust.} The thrust lands with great force and the target is knocked down. Take armour saves as normal and see whether the model suffers a wound.\\
\textbf{5–6 Kebab!} The thrust knocks the target back with titanic force, ripping apart armour and puncturing flesh. The attack ignores armour saves and you gain +2 to any Injury rolls. The victim is knocked backwards D6” and the attacker follows, staying in base contact. Any other models involved in the combat are separated and only the model which struck the blow and his target are still considered to be in combat. If the target collides with another model, the other model is hit once at S3.